Draft genomes of the three northern hemisphere blue mussel lineages: North and South European \emph{Mytilus edulis} and Mediterranean \emph{Mytilus galloprovincialis}.

### 2022-05-17 manuscript/ms_genomes.tex
unknown changes

We used \texttt{Orthofinder} (v2.5.2; \cite{Emms2015, Emms2019}) to find orthogroups and orthologue genes.
Species tree was inferred using the MSA method of \texttt{Orthofinder} and \texttt{IQTREE} tree inference (\texttt{-M msa -T iqtree}) \parencite{Emms2018, Nguyen2015}.

>>>>

We used \texttt{Orthofinder} (v2.5.2; \cite{Emms2015, Emms2019}) to find orthogroups and orthologue genes.
Species tree was inferred using the MSA method of \texttt{Orthofinder} \parencite{Emms2018} and \texttt{IQTREE} (v2.2.0\_beta; \cite{Minh2020}) tree inference.
